The Ranked Nearest Neighbour Interchange space

### 2019-05-02 paper.tex
why split counterexample in nni doesn't work in rnni

The proof presented in~\cite{Li1996} for Theorem~\ref{thm:split_nni} does not work for $\rnni$. \todo{because?}
Therefore, the following conjecture was raised~\cite{Gavryushkin2017}.

>>>>

The proof presented in~\cite{Li1996} for Theorem~\ref{thm:split_nni} does not work for $\rnni$.

%This part is mainly for myself, not sure whether it is important to have it in the paper
The main reason that the counterexample presented in~\ref{Li1996} works in $\nni$ is following:
Let $T_1$ and $T_2$ be two caterpillar trees.
If each taxon $a$ is repaced by a cherry $(a_1,a_2)$ in both trees $T_1$ and $T_2$, the resulting trees $T_1'$ and $T_2'$ have distance $d_{\nni}(T_1',T_2') = d_{\nni}(T_1,T_2)$ in the $\nni$ graph.
However, this does not work in $\rnni$.
Introducing new cherries means introducing new internal nodes with new ranks.
And a shortest path from $T_1$ to $T_2$ does not give a shortest path from $T_1'$ to $T_2'$, there will be some additional rank swaps needed for the internal nodes of the cherries.
% How do we assign the ranks to the new cherry nodes?
% We could give a precise example here, on 3 or 4 taxa (4 is the max, we can compute RNNI space for up to 8 taxa), because we know how the caterpillar trees with max distance look like.

Therefore, the following conjecture was raised~\cite{Gavryushkin2017}.
